% this createsactual paper business cards for q items as follows
 % sized 85*84mm (business cards)
 % 10 per a4 page
 % on Avery Zweckform C32010
\documentclass[a4paper,12pt]{article}\usepackage[]{graphicx}\usepackage[]{color}
%% maxwidth is the original width if it is less than linewidth
%% otherwise use linewidth (to make sure the graphics do not exceed the margin)
\makeatletter
\def\maxwidth{ %
  \ifdim\Gin@nat@width>\linewidth
    \linewidth
  \else
    \Gin@nat@width
  \fi
}
\makeatother

\definecolor{fgcolor}{rgb}{0.345, 0.345, 0.345}
\newcommand{\hlnum}[1]{\textcolor[rgb]{0.686,0.059,0.569}{#1}}%
\newcommand{\hlstr}[1]{\textcolor[rgb]{0.192,0.494,0.8}{#1}}%
\newcommand{\hlcom}[1]{\textcolor[rgb]{0.678,0.584,0.686}{\textit{#1}}}%
\newcommand{\hlopt}[1]{\textcolor[rgb]{0,0,0}{#1}}%
\newcommand{\hlstd}[1]{\textcolor[rgb]{0.345,0.345,0.345}{#1}}%
\newcommand{\hlkwa}[1]{\textcolor[rgb]{0.161,0.373,0.58}{\textbf{#1}}}%
\newcommand{\hlkwb}[1]{\textcolor[rgb]{0.69,0.353,0.396}{#1}}%
\newcommand{\hlkwc}[1]{\textcolor[rgb]{0.333,0.667,0.333}{#1}}%
\newcommand{\hlkwd}[1]{\textcolor[rgb]{0.737,0.353,0.396}{\textbf{#1}}}%
\let\hlipl\hlkwb

\usepackage{framed}
\makeatletter
\newenvironment{kframe}{%
 \def\at@end@of@kframe{}%
 \ifinner\ifhmode%
  \def\at@end@of@kframe{\end{minipage}}%
  \begin{minipage}{\columnwidth}%
 \fi\fi%
 \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
 \colorbox{shadecolor}{##1}\hskip-\fboxsep
     % There is no \\@totalrightmargin, so:
     \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
 \MakeFramed {\advance\hsize-\width
   \@totalleftmargin\z@ \linewidth\hsize
   \@setminipage}}%
 {\par\unskip\endMakeFramed%
 \at@end@of@kframe}
\makeatother

\definecolor{shadecolor}{rgb}{.97, .97, .97}
\definecolor{messagecolor}{rgb}{0, 0, 0}
\definecolor{warningcolor}{rgb}{1, 0, 1}
\definecolor{errorcolor}{rgb}{1, 0, 0}
\newenvironment{knitrout}{}{} % an empty environment to be redefined in TeX

\usepackage{alltt}  % because, why not?
\usepackage{longtable}  % for multi-page tables
\usepackage{array}  % for center, bottom vertical alignment in tables
\usepackage{calc}  % to easily identify dimensions etc.
\usepackage[T1]{fontenc}  % read in eur sim
\usepackage[utf8]{inputenc}  % allow accents etc in inputs
\usepackage[dvipsnames]{xcolor}





\usepackage[
  a4paper,
  height=54mm*5,  % 5 cards on top of one another
  width=85mm*2+10mm,  % 2 cards abreast, 10mm aisle
  vcentering,  % should be vertically centered
  hcentering  % should be horizontaly centered
  ]
  {geometry
}
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\begin{document}
\pagestyle{plain}
\setlength{\tabcolsep}{5mm}  % for margins and "aisle" margin between cards, fix by trial and error
%\newcolumntype{H}{>{\centering\arraybackslash\HUGE\ttfamily}m}  % need this because font size should be different for ID
\newcolumntype{H}{>{\centering\arraybackslash\Huge\sffamily}m}

\begingroup\Large
\begin{longtable}{H{72mm}m{0mm}m{75mm}}
  remote{\_{}}work{\_{}}family & \rule[-27mm]{0mm}{54mm} & By working from home, I can reconcile my work and family life without problems. \\
  work{\_{}}creativity & \rule[-27mm]{0mm}{54mm} & At work, I can give free rein to my creativity. \\
  free{\_{}}time{\_{}}work{\_{}}time & \rule[-27mm]{0mm}{54mm} & The distinction between work and free-time does not make a lot of sense to me. \\
  meaningful{\_{}}work & \rule[-27mm]{0mm}{54mm} & I spend my time at work doing something that matters. \\
  remote{\_{}}job{\_{}}done & \rule[-27mm]{0mm}{54mm} & What matters is not when or where I work, but that the job gets done. \\
  self{\_{}}motivation & \rule[-27mm]{0mm}{54mm} & It is my responsibility to motivate myself. \\
  enough{\_{}}staff & \rule[-27mm]{0mm}{54mm} & There is enough staff to get everything done that needs to be done. \\
  team{\_{}}work{\_{}}late & \rule[-27mm]{0mm}{54mm} & For my team, I’m happy to sometimes work late. \\
  best{\_{}}pressure & \rule[-27mm]{0mm}{54mm} & I perform best when I’m under pressure. \\
  work{\_{}}2{\_{}}live & \rule[-27mm]{0mm}{54mm} & I work to make a living. \\
  work{\_{}}life{\_{}}struggle & \rule[-27mm]{0mm}{54mm} & I am sometimes torn between the things I want to do in my personal life, and the things I should do for my career. \\
  own{\_{}}boss & \rule[-27mm]{0mm}{54mm} & I am my own boss. \\
  sleep{\_{}}well & \rule[-27mm]{0mm}{54mm} & I can sleep well, even when there are things left undone at work. \\
  live{\_{}}2{\_{}}work & \rule[-27mm]{0mm}{54mm} & I live to work. \\
  give{\_{}}best & \rule[-27mm]{0mm}{54mm} & I always try to give my very best. \\
  survival{\_{}}best & \rule[-27mm]{0mm}{54mm} & In the office, the best will succeed. \\
  whole{\_{}}person & \rule[-27mm]{0mm}{54mm} & In my work, I am valued as a whole person. \\
  stay{\_{}}til{\_{}}retirement & \rule[-27mm]{0mm}{54mm} & I’d be happy to stay in my current job until retirement. \\
  decide{\_{}}teammates & \rule[-27mm]{0mm}{54mm} & In my work, I decide with whom I work together. \\
  coop{\_{}}comp & \rule[-27mm]{0mm}{54mm} & In my line of work, cooperation gets you farther than competition. \\
  goal{\_{}}not{\_{}}means & \rule[-27mm]{0mm}{54mm} & At my work, I am given a goal, but I decide how to get there. \\
  emot{\_{}}aspects{\_{}}matter & \rule[-27mm]{0mm}{54mm} & In my work, emotional intelligence, empathy and being a good team player matter. \\
  recognition{\_{}}pay & \rule[-27mm]{0mm}{54mm} & Decent pay means that my work is being valued. \\
  clear{\_{}}guidelines & \rule[-27mm]{0mm}{54mm} & Clear guidelines make my work much easier. \\
  same{\_{}}rope & \rule[-27mm]{0mm}{54mm} & At the end of the day, employee and employer are tugging at the same rope. \\
  no{\_{}}tenure{\_{}}flexible & \rule[-27mm]{0mm}{54mm} & I do not have tenure at my job, but that keeps me flexible. \\
  exchange{\_{}}value & \rule[-27mm]{0mm}{54mm} & The worth of my work is determined by what others are willing to pay for it. \\
  use{\_{}}value & \rule[-27mm]{0mm}{54mm} & The worth of my work is determined by how useful it is to others. \\
  friends{\_{}}family & \rule[-27mm]{0mm}{54mm} & When I’m off work, I spend my free time with friends and family. \\
  free{\_{}}free{\_{}}time & \rule[-27mm]{0mm}{54mm} & I do not want my free time to be all planned. \\
  own{\_{}}interests & \rule[-27mm]{0mm}{54mm} & I take care of my own interests as an employee. \\
  hard{\_{}}structuring & \rule[-27mm]{0mm}{54mm} & I have a hard time structuring my work day. \\
  full{\_{}}part{\_{}}time{\_{}}dec & \rule[-27mm]{0mm}{54mm} & I decide whether I work full time, or part time. \\
  overwhelmed{\_{}}work & \rule[-27mm]{0mm}{54mm} & I often feel overwhelmed by all my work. \\
  support{\_{}}weaker & \rule[-27mm]{0mm}{54mm} & I am ready to support weaker co-workers. \\
  make{\_{}}concessions & \rule[-27mm]{0mm}{54mm} & To ensure the competitiveness of my employer, I am ready to make concessions. \\
  fit & \rule[-27mm]{0mm}{54mm} & To keep up at work, I make sure to stay physically fit. \\
  on{\_{}}street & \rule[-27mm]{0mm}{54mm} & Even if business takes a downturn, I won’t end up on the street immediately. \\
  passion{\_{}}long{\_{}}hours & \rule[-27mm]{0mm}{54mm} & If you’re passionate about your work, the long hours don’t matter. \\
  burden{\_{}}others & \rule[-27mm]{0mm}{54mm} & If you can’t give 100 percent, you don’t belong and you’re a burden to others. \\
  responsibility{\_{}}stress & \rule[-27mm]{0mm}{54mm} & Too much responsibility stresses me out. \\

  \textcolor{blue}{pseudonym: \_\_\_\_\_\_\_\_\_\_\_\_} & \rule[-27mm]{0mm}{54mm} & \textcolor{blue}{Email: \_\_\_\_\_\_\_\_\_\_\_\_ (if you'd like to receive the results)}\\

  \textcolor{red}{negative} & \rule[-27mm]{0mm}{54mm} & \textcolor{red}{Items you disagree with.} \\
  \textcolor{ForestGreen}{positive} & \rule[-27mm]{0mm}{54mm} & \textcolor{ForestGreen}{Items agree with.} \\
  \textcolor{Gray}{neutral} & \rule[-27mm]{0mm}{54mm} & \textcolor{Gray}{Items you do not understand, or are ambivalent about.} \\

  \textcolor{red}{1 card} & \rule[-27mm]{0mm}{54mm} & \\ %-5
  \textcolor{red}{2 cards} & \rule[-27mm]{0mm}{54mm} & \\ %-4
  \textcolor{red}{3 cards} & \rule[-27mm]{0mm}{54mm} & \\ %-3
  \textcolor{red}{5 cards} & \rule[-27mm]{0mm}{54mm} & \\ %-2
  \textcolor{Gray}{6 cards} & \rule[-27mm]{0mm}{54mm} & \\ %-1
  \textcolor{Gray}{7 cards} & \rule[-27mm]{0mm}{54mm} & \\ %0
  \textcolor{Gray}{6 cards} & \rule[-27mm]{0mm}{54mm} & \\ %1
  \textcolor{ForestGreen}{5 cards} & \rule[-27mm]{0mm}{54mm} & \\ %2
  \textcolor{ForestGreen}{3 cards} & \rule[-27mm]{0mm}{54mm} & \\ %3
  \textcolor{ForestGreen}{2 cards} & \rule[-27mm]{0mm}{54mm} & \\ %4
  \textcolor{ForestGreen}{1 card} & \rule[-27mm]{0mm}{54mm} & \\ %5

  \textcolor{Brown}{array-dim: desirable-1} & \rule[-27mm]{0mm}{54mm} & \textcolor{brown}{1st run: What would you \emph{like} to be able to say about your job?} \\
  \textcolor{Brown}{array-dim: probable-2} & \rule[-27mm]{0mm}{54mm} & \textcolor{brown}{2nd run: What will you \emph{probably} to be able to say about your job?} \\

  \textcolor{Brown}{array-dim: desirable-2} & \rule[-27mm]{0mm}{54mm} & \textcolor{brown}{2nd run: What would you \emph{like} to be able to say about your job?} \\
  \textcolor{Brown}{array-dim: probable-1} & \rule[-27mm]{0mm}{54mm} & \textcolor{brown}{1st run: What will you \emph{probably} to be able to say about your job?} \\

\end{longtable}
\endgroup

\end{document}
